\section*{People Power \& Conflict Evolution}

There is little empirical evidence that protests should or should not ``work" in contexts of high violence at the sub-state level. There are several possible logics linking protest and violence between armed groups.

First, there might be no relationship between protests and violence. Protest might have other benefits and thus persist for reasons outside of the stated goals driving protest organizers. For example, non-violent activism via protest can stimulate community between survivors of violence and foster a sense of purpose and belonging in the midst of crisis. Additionally, protests against insecurity and issues of violence might be targeted at both types of armed actors (i.e. the state and the non-state challenger), these actors could respond to protests through other means outside of violent strategy. Non-state armed groups might make public appeals to civilians, saying that they are there for civilians' protection. Similarly,  governments can respond with media campaigns, speeches, or through a general effort to try to divert political attention from violent events. A second mechanism driving a null relationship between protests and violent events is the high level of risk for protestors. Following a protest, participants might be targeted because of their activism, possibly resulting in fewer protests over time but with no clear consequences for violence between armed groups.

Second, protest participants might achieve their stated aims and decrease violent contestation in their region. If protests successfully demand that the government invest greater resources in the prevention of violence, then we would expect fewer incidents of violence following protests. If protests also demand that non-state actors stop warfare with the state, this manifests as a public disapproval of attempts by the non-state group to coerce or control the civilian population. With enough discontent, protests disrupt the ability of non-state actors to operate in their region.

Finally, protest could lead to an increase in violence. As violence between armed actors (state and non-state) increases, non-state actors often victimize civilians to highlight the government's inability to protect the population. Even if protestors demand a non-violent solution to warfare, a final plausible logic connecting protest and violence is that protest raises the cost of government inaction so that government armed actors are more likely to visibly fight hard in the next round of contestation. This logic would suggest an antagonistic government actor, one who is politically motivated to demonstrate competency through violent policy.


