\section{Editor}

\begin{enumerate}
	\item Though this piece came to me as a methods paper, I agree with R. 2 that the best approach is probably to focus foremost on the substantive motivation, lay out your original theoretical perspective, show how that determines the choice of methodology, and explain what you found. That dovetails with R. 3's good suggestions about approaching the presentation, and with R. 1's critiques about the clarity of the central aim of the paper. The key questions are boiled down succinctly by R. 3 who asks that you clarify, ``what are the consequences of these limitations [that you identify in previous approaches]? What don't we understand that, at the end of this article, we will understand better?''
	\begin{itemize}
		\item \textcolor{blue}{ \emph{
		We clarify the purpose of the paper, principally through a complete re-write of the introduction and theoretical section. In the introduction we now begin by explaining how existing dyadic analyses of conflict, which tend to focus primarily on non-state actor vs. state dyads, miss important actors and interactions relevant to understanding conflict processes as whole. We illustrate this point with historical anecdotes. In the new theoretical section we now begin with first principles on the motivations and attributes of armed groups, drawn from the literature, to explain violent behavior during conflicts. While the focus on the rebel-state dyad is important, it overlooks how interactions between actors might inform future behavior. We then explain how a network approach flows from the motivations and attributes in the dyadic literature, and how this approach allows us to systematically examine the influence of relationships and actors' interactions on levels of conflict over time.  }}
	\end{itemize}	
	\item In addition, though you certainly sought to avoid wading into the latent space ``vs.'' (T)ERGM ``debate'', I agree with R. 1 that more discussion of your preference for one over the other is called for. To me the most straightforward (if labor intensive), and most transparent way to handle this is to consider TERGM as a robustness check in an appendix.
	\begin{itemize}
		\item \textcolor{blue}{ \emph{
		Section A.1.11 presents the results when estimated through a TERGM that includes endogenous terms for reciprocity and a geometrically weighted edgewise shared partners term that enables us to get at transitivty. The results from the TERGM and AME are similar. 
		}}
	\end{itemize}		
\end{enumerate}