\section{Reviewer 2}

\subsection{Major Comments}

\begin{enumerate}
	\item  What I find interesting and publication-worthy about this paper is the substantive insights about actors, their effects of one another, and the entry of new conflict participants. This is the part that constitutes the core of the contribution, not the methodological approach. I would support publication of this manuscript as a substantive piece that is driven by an empirical puzzle and analyzed using an appropriate method. The manuscript, as it is currently written, sells itself as methodological fix rather than a substantive advance on our knowledge of civil war dynamics. I think this is a poor framing/presentational choice and sells the contribution short. It also seems backwards.  I would start with a substantive puzzle, build a theoretical model of interaction among actors of different types, derive predictions, and only then get to the method and testing. As it is, the actual substantive story does not start until p. 8--this is where I would start the paper.
	\begin{itemize}
		\item \textcolor{blue}{ \emph{
		Thank you for this helpful feedback! We appreciate your interpretation of our contribution and have worked hard to use these core insights to rewrite the front end of the paper. Specifically, we have rewritten the introduction to better set up the primary empirical puzzle of ``Who fights who and when?" In the new theoretical section we now begin with first principles on the motivations and attributes of armed groups, drawn from the literature, to explain violent behavior during conflicts. We then explain how a network approach flows from the motivations and attributes in the dyadic literature, and how this approach allows us to systematically examine the influence of relationships and actors' interactions on levels of conflict over time. In doing so, we have also more deeply incorporated literature by Will Moore and others who have highlighted the importance of interactions to explain violent behavior. 
		}}
	\end{itemize}	
	\item I  especially like the part about new participant entry. Why would we expect that an entry by a new participant would affect the conflict dynamics?  What types of participants are likely to enter an ongoing conflict? What possible relationships may a new participant have to the current participants?  Why would an entry of a new participant increase outbidding?  I think the authors have some interesting ideas, but these need to be developed much further. I would like to be presented with a well-grounded theoretical story related to the entry of a new participant in an ongoing conflict.
	\begin{itemize}
		\item \textcolor{blue}{ \emph{
We attempt to address all of these questions about new actor entry.
\begin{itemize}
\item As we discuss on page 7, entries by a new participant can increase the likelihood of conflict by weakening the government, leading to the government becoming more violent to restore credibility, or by imperiling the resource bases of rebel actors.
\item As we address in footnote 4, page 8, we do believe that entrants in a civil conflict will not, on average, be more powerful or violent than groups already in a conflict, but that the entrants of particularly strong and violent actors are what risk an escalation.
\item We discuss on pages 8-9 how a new entrant into a civil conflict could be tacit allies with certain groups, attack other groups, and have no direct relation to some groups.
\item We discuss (first paragraph, page 10) how outbidding in particular is likely to happen to groups that both rely on civilians for support and have similar constituencies, when a new group is stronger, more aggressive, or more successful than existing groups.
\end{itemize}
		}}
\end{itemize}

\item Instead, the current draft spends the first 7 pages trying to convince the reader that the study of civil war is important and that actors in a civil war may affect one another's actions--both of these ideas are non-controversial. Then there is a lengthy discussion of network terms and methods, which I would move to the research design section.  I would also move the history of Nigerian conflict to the appendix, is distracts from the flow.	
	\begin{itemize}
		\item \textcolor{blue}{ \emph{
		We addressed this feedback in three ways. First, we shortened the introduction and re-wrote it it to be concise, clearer about the goals of the paper and, we hope, more compelling. Second, we removed the section on network terms (including the ``stylized network'' graphic) from the main body of the paper and added it to the appendix. Given the substantive orientation of the revised paper, we now see this section as distracting, though useful for those unfamiliar with network terminology. Third, we have moved, edited and shortened the section summarizing the Nigerian case. We now present this information as part of our Data section, because we believe it is important to discuss the case in order to illuminate both our case selection justification as well as provide context for our model and, later, our findings. We hope that these changes remedy the paper's flow problem.
		}}
	\end{itemize}		
\end{enumerate}