\section*{Introduction}

Since 1946 more than half of the countries in the international system have experienced a civil war \citep{gleditsch:etal:2002}, and although wars between countries have waned in recent years, there are a growing number of intrastate conflicts \citep{pettersson:wallensteen:2015}. These types of conflicts have proven to be costly -- civil wars in countries as diverse as the Ukraine, Syria, and Nigeria have been some of the most deadly conflicts of the post-Cold War period. The prevalence and costliness of such conflicts have resulted in the development of a rich literature on the causes and consequences of civil war.\footnote{For example, see \citet{salehyan:2008,lacina:2014}.} In fact, \citeauthor{fearon:2003}'s influential 2003 article exploring the conditions under which countries are most at risk for civil war has been cited over 6,000 times, underscoring the value placed on understanding when, and why, conflicts begin. Such research agendas encompass the study of conflict onset and conflict prediction, and have been formative to scholarship on conflict processes more broadly, leading to investigation of not just how conflicts begin, but how they develop after initiation. Accordingly, researchers are now concerned with a wide variety of analyses on armed non-state actors' attributes, coordination, and relationships \citep{cunningham:2006,bakke:etal:2012, findley:rudloff:2012,akcinaroglu:2012}
% \footnote{According to Google Scholar at the time of this writing.}
% from SM: the last sentence in the paragraph above was just hard to read so i shortened it but kept the references
% , spoiler groups and veto-players \citep{cunningham:2006}, and rebel interdependencies and civil war outcomes \citep{akcinaroglu:2012}. 

While these fine-grained approaches to the study of intrastate conflict signal a productive shift in the literature, most of these studies remain rooted in a dyadic research design. Importantly, this design has allowed for researchers to move away from state-centric analysis. Building on the work of \cite{cunningham:etal:2009}, \citet[p. 880]{akcinaroglu:2012} notes, ``Existence of multiple rebel groups means we can no longer understand civil wars with a sole focus on state attributes. In fact, the government's strategies leading to victory, defeat, or continuation of war can only be understood in relation to the rebel group/groups it is fighting.'' Dyadic research designs have allowed for a closer examination of cases in which the government fights many different armed actors, rather than a single insurgent movement. Although such studies make significant theoretical and empirical contributions they are limited by the assumption of independence between dyads that is explicit in empirical dyadic analyses. In turn, current research has yet to provide full consideration of the interconnected multi-actor dynamics that characterize recent examples of intrastate conflicts;  a notable restriction given that by 2003 over 30\% of ongoing civil wars involved multiple dyads in conflict with one another \citep{harbom:etal:2008}. 

The contribution of this study is to bridge this disconnect and model civil conflict processes in a way that is reflective of their empirical form. Namely, we argue that intrastate conflicts are best understood as a single complex system composed of multiple actors in conflict with one another rather than as a set of independent, dyadic events. Accordingly, we conceptualize armed actors and battles as nodes and linkages in a network wherein the actors and their relationships change over time. This framework allows us to estimate the relationships that evolve between actors in a conflict network in order to predict the occurrence of battles between groups within the system.  In doing so, our paper is the first to apply an empirical-based network methodology to the study of civil conflict evolution. Our network approach, which we employ to investigate civil conflict in Nigeria, significantly outperforms traditional dyad-group approaches at predicting the occurrence of battles between groups in an out-of-sample context. Finally, our findings yield theoretical implications for the study of civilian victimization and conflict occurrence, as well as insights about how the entrance of particularly aggressive actors can decisively alter the trajectory of conflict.

%We accomplish this by introducing a network-based approach that allows us to estimate the interdependencies between actors within an intrastate conflict system even as the composition of actors changes over time

%Systems of this sort have long been studied in other fields such as sociology, where researchers have argued that to understand an actor's (or group's) behavior it is necessary to understand the system in which the actor is enmeshed \citep{granovetter:1973,wellman:1982,wasserman:faust:1994}. Many of the questions that conflict scholars are interested in require a careful application of these lessons. For example, can the actions of a particular actor lead to greater levels of violence between other actors in the system? How does a government crackdown on one group affect the activities of other challenger groups? Grappling with any of these questions requires developing a methodological approach that accounts for dependencies between actors. We accomplish this by introducing a network-based approach that allows us to estimate the interdependencies between actors within an intrastate conflict system even as the composition of actors changes over time. In doing so, our paper is the first to apply an empirical-based network methodology to the study of civil conflict evolution. 

%To study how violence evolves, we turn to the Nigerian case during 2000-2016. Throughout this time period, Nigeria has seen the rise of multiple armed non-state actor groups. In the southern delta region, armed actors such as the Movement for the Emancipation of the Nigerian Delta (MEND) have battled the government for control of oil production. Boko Haram, potentially the most well known of these groups, has caused massive devastation both to human life and infrastructure in the Northern regions of the country. Accordingly, Boko Haram has challenged the government's ability to keep order and protect civilians. By using a network approach, we can better understand and predict these dynamics in Nigeria. In particular, this approach yields insights about how the introduction of a violent challenger can alter the trajectory of the conflict. We find that Boko Haram's entrance into the civil war leads to an increase in violence even in unrelated dyads. Our approach, which accounts for the networked nature of conflict in Nigeria, significantly outperforms traditional dyad-group approaches at predicting which groups will have battles and when.


%For example, in the current Syrian civil war, Bashar al-Assad's government is fighting against the Islamic State and multiple militarized opposition groups (e.g., the Free Syrian Army, Jaysh al-Islam, Ahrar al-Sham and others). Each of these actors is often involved in battles both with the government and amongst themselves. In other regions, like Mexico, we observe drug trafficking organizations (DTOs) vying both for political influence and territorial control against government actors and other DTOs.  Complex systems of conflict dynamics such as those can be found in countries as varied as India, Colombia, and Nigeria. Many researchers recognize that such cases require a consideration of how non-state groups relate to one another and the government \citep{fotini:2012,cunningham:2014}. Empirical research on intrastate conflict, however, has done little to recognize that the intrastate conflicts many countries are embroiled in are understood best as a single complex system composed of multiple actors in conflict with one another rather than as a set of independent, dyadic conflicts.


