\section*{Existing Approaches: People Power \& Conflict Evolution}

More often than not, stories of armed conflict, war, or widespread criminal violence shine a spotlight on those actors who initiate injustices or wield power through collective violence against a given population. Recently, however, this narrative has begun to change. With the various uprisings across the previous 5 years--the Tunisian revolution, the Egyptian revolution, the Syrian Civil War, the Yemen revolt, the 2013 protests in Turkey, and the 2014 protests in Venezuela (just to name a few)--attention has shifted to recognize the power of the population to influence environments of extreme violence and repression.

A diverse range of conflictual episodes occur around the world: coups, civil wars, drug wars, refugee crises, border disputes. While media attention might focus on civilians fleeing or to cooperating with whichever armed actor wields the greatest power in their region, a truer picture reveals a vast range of civilian responses to violence.  Mass anti-regime movements are an important form of civilian response in some cases but civilians might also engage at the local level through self-defense forces, community watch groups, civil society efforts, or nonviolent campaigns in their home town. 

%The study of internal war and intrastate conflict comprises an important and developing literature within political science, with principal focus on the onset, evolution, and termination of civil conflict. Studies on conflict onset have focused on identities, ethnicities, and economic grievances as causes of conflict \citep{collier04b, fearon03b, cederman10a}. Research focusing on conflict evolution primarily theorizes about the behavior of rebel groups and state actors \citep{humphreys06, stathis2006logic, fearon07, lyall09, weinstein07}. Related work on the micro-processes of civil conflict has assessed how the \textit{type} of conflict varies across cases \citep{kalyvas2001new, kalyvas2010international, lacina2006explaining}. Studies on civil war duration and termination typically focus on state-level attributes \citep{hegre2004duration, karl2004dynamics, buhaug2002geography} and the characteristics of non-state challengers \citep{cunningham09} to predict when a conflict will end. 

While these studies have made critical progress in the field of intrastate violence, analyses on the intersection of armed conflict and civilian life are gaining relevance \citep{collier1999, ghobarah03, lyall2013, fair2013}. Interestingly, investigations into the micro-processes of civil conflict highlight the wide variation in violence against civilians that rebels adopt during civil conflicts \citep{humphreys06, fearon07, lyall09, weinstein07}, including why armed groups target civilians \citep{balcells10}, strategies between non-state actors and civilians \citep{kaplan2013protecting,arjona2011social}, and how different targeting strategies influence civilian displacement \citep{steele2009seeking}. This focus on the effects of violence on civilian life is important but does not address the other side of the civilian puzzle, which is to assess whether civilians can mobilize to change the course of war. 

Compared to the high number of studies focusing on structural, economic, and historical motives for the duration and intensity of conflict, existing research has largely neglected the role of protest in influencing the behavior of armed actors. A large body of research has explored the origins of collective action and mobilization, (Gurr 1970; Opp 1988, Tarrow 1994, Tucker 2007) and recent scholarship has assessed the effectiveness of ``maximalist campaigns" \citep{chenoweth2011civil} to show that countries are more likely to be democratic following nonviolent campaigns. However, as articulated by \cite{celestino2013} even the macro-level relationship between nonviolent campaigns and state-level outcomes such as democracy or regime transitions remains unclear. Importantly, \cite{celestino2013} show that nonviolent campaigns destabilize regimes, but that the trajectory of peace and democracy following such campaigns is conditional on the precise actions employed by campaign organizers. 

Building on the research agenda motivated by these macro-level studies, we investigate the link between nonviolent action and violence at the local level. The focus of this study is two-fold. First we discuss the importance of predicting conflict processes through a network approach. In doing so, we suggest that networks of conflict represent a meaningful outcome of interest and depart from the great majority of the literature which focuses on dyadic outcomes to measure conflict intensity or duration. Second, we contribute to a growing scholarship interested in whether or not people-power driven actions and campaigns influence trajectories of violence and stability. 


