\section*{Conclusion}

Intrastate conflicts are often much more complex than Manichaean struggles between a government and a unified opposition. More and more, they involve a number of independent actors with interdependent behavior. This complexity highlights avenues for further research into how interdependencies in actor behavior can be characterized. In this work, we have presented a network based framework that can be used to uncover underlying structure in conflict systems. By utilizing this approach, we are able to markedly improve our ability to predict and forecast battles between armed groups in the case of Nigeria. 

The improved predictive performance of our network based approach is a result of the fact that there was significant structure underlying the Nigerian conflict system. We presented evidence for the occurrence of first, second, and third order dependence patterns. The implication of first order dependence patterns is that there are latent actor attributes not accounted for by our model specification that could be used to explain why some actors are more conflictual than others. Interestingly, one of the more striking findings is that the Fulani militia is particularly more active in engaging in battles than the exogenous sender, receiver, and dyadic variables in our model would predict. This highlights the opportunity for further research into understanding what latent attribute may be driving that inflated conflictual behavior. Our findings with regards to second order dependencies highlights the strong role of reciprocity in this network. This is a finding common in the interstate conflict literature and the case of Nigeria, at least, highlights that this type of pattern persists in intrastate conflict as well.  Last, in our visualization of the multiplicative effects used to capture third order dependencies we find strong evidence that groups of actors in this system form various communities of conflict. Notably, groups in the Middle Belt of Nigeria form a geographically concentrated conflict clique. Each of these dependencies points to the fact that there is underlying structure to the set of dyadic interactions that we observe in this network even after accounting for the effects of exogenous covariates. 

Further by accounting for these dependencies, we are able to more accurately test exogenous actor and dyadic level explanations for conflict. First, because of our ability to estimate a network model in which the actor composition is changing over time, we can assess the impact that particular actors such as Boko Haram had on the system. Doing so enabled us to find that the entrance of this single actor profoundly changed interactions across the system. A question that this raises for future research is whether or not we can more formally study why some actors have stronger effects on shaping interactions across a network than others. Additionally, our results highlight the role that civilian victimization can play in further perpetuating violence. Even after controlling for network related dependencies within this system, we find that actors who target civilians are more likely to receive and send conflict themselves. Relatedly, we find little evidence that civilian led protest against a particular actor changes that actor's likelihood in initiating conflict. To some extent, these findings showcase the limitations of civilian populations to change the behavior of actors in environments of extreme violence. 

However, the findings with regards to the role of civilian victimization and civilian riots/protests should not necessarily be generalized beyond the Nigerian case. Nigeria may be unique for several reasons, its 150 million people are divided almost equally between Muslims and Christians. Further, Nigerians split into even finer divisions based on tribe, of which there are over 200 in the country. Nonetheless, what we have shown is that to account for intrastate conflict dynamics in environments as complex as these, scholars need to move beyond a priori assumptions of dyadic independence. Doing so enables us to account for endogenous structures that develop within these systems. 

%Our study supports two future avenues of research at the subnational level. First, scholars of intrastate violence should carefully explore the role of interdependencies in armed conflict settings. Second, one of the key contributions of our study is in our ability to disaggregate which actors target civilians, and which civilians protests against armed actors.  More micro-level analysis is needed to further explore the enabling conditions for civilian mobilization in contexts of severe violence and insecurity. Finally, our study has two testable implications for future research at the cross-national level: (1) our findings suggests that civilians face greater barriers to organizing and are less effective at mobilizing in multi-party conflict settings. This could be tested in a cross-national framework to analyze whether an increase in the number of rebel actors is associated with less (or less efficacious) protest activity in a given country; (2) our study also suggests that civilian predation is more likely in multi-party conflict settings. 

