\clearpage
\section*{Discussion}

\subsection*{Intrastate Conflict as a Dynamic Network}

Intrastate conflicts are often more complex than Manichaean struggles between a government and a unified opposition. More and more, they involve a number of actors operating in an environment where interactions can be interdependent. The improved predictive performance of our network approach is a result of the fact that there is significant network based structure underlying the Nigerian conflict system. Apart from pointing to the utility of taking network patterns into account, our study also highlights how we can use the AME model to uncover the types of first, second, and third order dependence patterns that emerge. 

The implication of first order dependence patterns is that there are latent actor attributes not accounted for by our model specification that could be used to explain why some actors are more conflictual than others. Interestingly, one of the more striking findings is that the Fulani militia is particularly more active in engaging in battles than the exogenous sender, receiver, and dyadic variables in our model would predict. This highlights the opportunity for further research into understanding what latent attributes may drive such inflated conflictual behavior. Our findings with regards to second order dependencies demonstrate the strong role of reciprocity in this network. This reflects a common intuition from the interstate conflict literature and our study of Nigeria highlights that this type of pattern also persists in intrastate conflicts.  Last, our visualization of the multiplicative effects captures third order dependencies and shows strong evidence that actors in this system form various communities of conflict. Each of these dependencies points to the fact that there is an underlying structure to the set of dyadic interactions that we observe in this network even after accounting for the effects of exogenous covariates. Since these patterns play a role in the data-generating process of intrastate conflict, our approach out-performs more traditional frameworks that ignore such dependencies.

\subsection*{Implications for Future Research}

By utilizing information about dependencies between actors to accurately consider how conflicts develop over time, we are also able to more accurately test exogenous actor and dyadic level explanations for conflict. First, because we are able to estimate a network model in which actor composition changes over time, we can assess the impact that particular actors such as Boko Haram have on the system. We find that the entrance of this single actor profoundly changed interactions across the system. Boko Haram's entrance does not simply increase conflict \emph{directly}, it also is associated with a marked rise in violence in the dyads that \emph{do not include Boko Haram.} This raises an important question for future research which is whether or not we can formally study why some actors have stronger effects on shaping interactions across a network than others. 

Our present study is necessarily limited in that we retroactively observe the influence of Boko Haram on the conflict network. However, our results dovetail with current findings about Boko Haram's rise and expansion and provides insights for defining key actors in other conflict settings. First, we have shown that Boko Haram is particularly violent and targets both the government and civilians. \citet{weeraratne:2017} argues that a key determinant of Boko Haram's rise is their rapid increase in the use of violence against societal actors, government armed groups, religious communities, and civilians. \citet{osumah:2013} details how the targeting strategies of Boko Haram has weakened the government's security apparatus and heightened tensions across the country. Second, there is evidence to suggest that Boko Haram was particularly well-organized and well-resourced even in the first few years of its operation \citep{osumah:2013}. Group-level attribute data would provide a way to test whether groups that are highly organized, well-resourced, and target a wide range of actor types are likely to have a broad affect on sub-national level violence, similar to the Boko Haram's influence in Nigeria.

Additionally, our results highlight the role that civilian victimization can play in further perpetuating violence within a network context. Even after controlling for network related dependencies within this system, we find that actors who target civilians are more likely to receive and send conflict themselves. Relatedly, we find little evidence that civilian led protest against a particular actor changes that actor's likelihood in initiating conflict. To some extent, these findings showcase the limitations of civilian populations to change the behavior of actors in environments of extreme violence. Future research should compare and contrast these findings beyond the Nigerian case to better illuminate the networked nature of civilian mobilization in conflict environments. The findings with regards to the role of civilian victimization and civilian riots/protests might not generalize beyond the Nigerian case. Nigeria may be unique for several reasons, its 150 million people are divided almost equally between Muslims and Christians. Further, Nigerians split into even finer divisions based on tribe, of which there are over 200 in the country. 

\section*{Conclusion}

Our study has embraced the complexity of multi-actor conflicts, rather than discounted it. We have shown that network dynamics help explain the occurrence of violence between groups over time, even as actors enter and exit the conflict. We have demonstrated how key, violent actors can increase violence within a network system. Additionally, our approach achieves a longstanding goal of conflict studies: to accurately predict violence over time. Our approach offers important insights into how conflict studies can utilize methodological innovations to expand theoretical inquiry. 

These contributions are not without their limitations. While our study affirms the utility of ACLED data efforts, more actor-level characteristics are needed to fully engage the rich literature on civil war dynamics. Such data would enable even more precise investigation of covariates of interest for determining changes in rebel group behavior over time. Second, though our study has revealed meaningful findings with respect to key covariates such as civilian victimization, more research is needed to explore the generalizability of such results. We hope this study motivates future work that more fully considers the conflictual behavior of armed actors in complex settings.
